\documentclass[letterpaper,11pt]{article}

\usepackage[top=0.5in, bottom=0.35in, left=0.55in, right=0.55in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Colors
\definecolor{sectionblue}{HTML}{2077B4}

% Remove page numbers
\pagestyle{empty}

% Reduce spacing
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\parindent}{0pt}

% Disable word hyphenation (no splitting words across lines)
\hyphenpenalty=10000
\exhyphenpenalty=10000
\tolerance=2000
\emergencystretch=1em

% Custom section command
\renewcommand{\section}[1]{%
  \vspace{5pt}%
  {\large\bfseries\color{sectionblue}#1}\\[-6pt]%
  {\color{sectionblue}\rule{\textwidth}{0.8pt}}%
  \vspace{1pt}%
}

% Compact itemize
\renewenvironment{itemize}{%
  \begin{list}{\textbullet}{%
    \setlength{\leftmargin}{1.5em}%
    \setlength{\itemsep}{1pt}%
    \setlength{\parsep}{0pt}%
    \setlength{\topsep}{1pt}%
    \setlength{\partopsep}{0pt}%
  }%
}{\end{list}}

\begin{document}

% ==================== HEADER ====================
\begin{center}
{\LARGE\textsc{\textbf{Tianjiao Zheng}}}\\[2pt]
Berkeley, CA \enspace|\enspace 510-292-1953 \enspace|\enspace jiaojiao1210@gmail.com
\end{center}

% ==================== PROFESSIONAL SUMMARY ====================
\section{Professional Summary}

Senior Credit Analyst with 5+ years of commercial banking experience in credit underwriting, loan structuring, and portfolio management. Proven ability to evaluate complex borrower profiles across business, individual, and non-profit sectors while managing client relationships and ensuring covenant compliance. Committed to high-quality client service while driving loan and deposit growth. Spearheaded a bank-wide risk platform migration that streamlined loan processing and portfolio monitoring across multiple regions.

% ==================== WORK EXPERIENCE ====================
\section{Work Experience}

% --- Bank of Marin ---
\textbf{Senior Credit Analyst} \hfill \textbf{06/2023 -- Present}\\
\textbf{Bank of Marin} \hfill Oakland, CA
\begin{itemize}
  \item Underwrote business credit requests by analyzing financial statements, cash flow projections, and industry conditions to assess creditworthiness and identify risk drivers across a diversified middle-market portfolio.
  \item De facto portfolio manager---managed client relationships and conducted annual portfolio reviews to validate credit quality, enforce covenant compliance, and maintain regulatory reporting accuracy.
  \item Structured and negotiated business credit facilities including term loans, revolving lines, and letters of credit, with loan covenants and collateral requirements tailored to business, individual, and non-profit borrowers.
  \item Prepared credit memos and approval packages for new loans, renewals, extensions, and modifications; presented recommendations to senior management.
  \item Led cross-functional implementation of Abrigo risk platform, streamlining loan origination and portfolio monitoring across multiple regional offices.
\end{itemize}

\vspace{1pt}

% --- Bank of the Orient: Credit Analyst ---
\textbf{Credit Analyst} \hfill \textbf{03/2021 -- 05/2023}\\
\textbf{Bank of the Orient} \hfill San Francisco, CA
\begin{itemize}
  \item Evaluated borrowers' financials while assessing industry risks, collateral adequacy, and loan structuring options to support credit decisions.
  \item Prepared credit memos and presentations summarizing borrower risk profiles, loan structures, and repayment analyses for loan committee review and approval.
  \item Monitored borrower financial health and covenant compliance; identified early warning signals and implemented risk mitigation strategies to preserve portfolio quality.
  \item Coordinated with sales, credit, and senior management teams to drive efficient credit decisions and support strategic portfolio growth.
\end{itemize}

\vspace{1pt}

% --- Bank of the Orient: Loan Assistant ---
\textbf{Loan Assistant} \hfill \textbf{10/2020 -- 03/2021}\\
\textbf{Bank of the Orient} \hfill San Francisco, CA
\begin{itemize}
  \item Coordinated data collection and analysis to produce thorough loan packages meeting internal credit policy and regulatory standards; examined legal and credit documents for accuracy and completeness.
  \item Built relationships with clients, brokers, title companies, and insurance providers to ensure seamless loan closings, funding, and ongoing transaction support.
  \item Ordered and tracked appraisals, title reports, credit reports, and flood certifications to support underwriting timelines and ensure complete loan file readiness.
\end{itemize}

% ==================== EDUCATION ====================
\section{Education}

\textbf{Bachelor of Science: Economics} \hfill \textbf{2019}\\
University of California -- San Diego \hfill San Diego, CA

% ==================== SKILLS ====================
\section{Skills}

\textbf{Core Competencies:} Credit Risk Analysis, Loan Origination \& Structuring, Portfolio Management, Financial Modeling, Covenant Design, Regulatory Compliance, Client Relationship Management\\[2pt]
\textbf{Tools \& Technology:} S\&P Capital IQ, Abrigo, LexisNexis, CoStar, Experian, SQL, Python, R, Tableau, Excel

\end{document}
